---
title: "Project1 Text Mining"
author: "Ambra"
date: "February 26, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Chess Tournament
In this project, you're given a text file with chess tournament results where the information has some structure. Your job is to create an R Markdown file that generates a .CSV file (that could for example be imported into a SQL database) with the following information for all of the players:
Player's Name, Player's State, Total Number of Points, Player's Pre-Rating, and Average Pre Chess Rating of Opponents.
For the first player, the information would be:
Gary Hua, ON, 6.0, 1794, 1605
1605 was calculated by using the pre-tournament opponents' ratings of 1436, 1563, 1600, 1610, 1649, 1663, 1716, and dividing by the total number of games played.


```{r Chess Table}

chess<- readLines("C:\\Users\\ambra\\Desktop\\Data 607\\W4\\tournamentinfo.txt")
class(chess)

library(stringr)

##Remove headings 

chess<- chess[c(-1:-4)]


##Extract player's name

NAME<-str_trim(unlist(str_extract_all(chess, "[[:upper:]]{2,}\\s\\w+(\\s\\w+)?\\s?\\w+?\\s?[[:punct:]]?\\w*")))  


##Extract state

state<- unlist(str_extract_all(chess, "(ON|MI|OH)\\s\\|"))
STATE<- str_trim(unlist(str_replace_all(state, "\\|", "")))

##Extract total number of points

points<- unlist(str_extract_all(chess, "\\|\\d\\.\\d\\s"))

POINTS<- str_trim(unlist(str_replace_all(points,"\\|", "")))

##Extract pre-rating

prerating<- unlist(str_extract_all(chess,"R:\\s?\\s\\d{3,}P?"))
prerating2<-str_trim(str_replace_all(prerating, "R:\\s?\\s", ""))
PRE_RATING2<-str_trim(str_replace_all(prerating2, "P$", ""))

PRE_RATING<- sapply(PRE_RATING2, as.numeric)

y<- as.data.frame(chess)
##Extract opponents for each player


opponents<- apply (y, 1, function(x) (unlist(str_extract_all(x,"(W|D|L)( )+\\d{1,3}"))))

##Remove 0 characters from vector

opponents1<- opponents[lapply(opponents,length)>0]

##remove W|D|L

opponentsindex<- str_extract_all(opponents1,"\\d{1,3}")
library(plyr)
opponentsdf<- ldply(opponentsindex, rbind)
opponentsdf1<- sapply(opponentsdf, function(x) as.numeric(as.character(x)))


chessdf<- data.frame(cbind(NAME, STATE, POINTS, PRE_RATING))

chessdf["X1"]<-opponentsdf1[,1]
chessdf["X2"]<-opponentsdf1[,2]
chessdf["X3"]<-opponentsdf1[,3]
chessdf["X4"]<-opponentsdf1[,4]
chessdf["X5"]<-opponentsdf1[,5]
chessdf["X6"]<-opponentsdf1[,6]
chessdf["X7"]<-opponentsdf1[,7]

rownames(chessdf)<- seq_len(nrow(chessdf))


for (i in 1:nrow(chessdf)){
  
        chessdf$X1[i]<-as.numeric(as.character(chessdf$PRE_RATING[chessdf$X1[i]]))
        chessdf$X2[i]<-as.numeric(as.character(chessdf$PRE_RATING[chessdf$X2[i]]))
        chessdf$X3[i]<-as.numeric(as.character(chessdf$PRE_RATING[chessdf$X3[i]]))
        chessdf$X4[i]<-as.numeric(as.character(chessdf$PRE_RATING[chessdf$X4[i]]))
        chessdf$X5[i]<-as.numeric(as.character(chessdf$PRE_RATING[chessdf$X5[i]]))
        chessdf$X6[i]<-as.numeric(as.character(chessdf$PRE_RATING[chessdf$X6[i]]))
        chessdf$X7[i]<-as.numeric(as.character(chessdf$PRE_RATING[chessdf$X7[i]]))
        
}

chessdf["AVERAGE_PRERATING"]<-  round(rowMeans(chessdf[, 5:11], na.rm = TRUE ), digits = 0)

library(htmlTable)

htmlTable(chessdf)

finalchessdf<- chessdf[-(5:11)]

write.csv(finalchessdf, file="C:/Users/ambra/Desktop/Data 607/W4/TournamentInfo.csv")

```

